An Airdrop That Preserves Recipient Privacy

### 2019-01-12 paper/paper.tex
edits

\begin{proof}
The simulator takes $(c, t)$ as input and outputs the simulated transcript
$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
\begin{alg}
\> choose random $\hat{c}_1, \hat{c}_2 \rgets \GG,\ \ \ell \rgets \primes$, and
$\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
\> set $c_1 \gets \hat{c}_1^\ell$ and $c_2 \gets \hat{c}_2^\ell$, \AlgSep
\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
\lnum \label{ln:randv}
\> choose random $\hat{\rv} \rgets \range{2^{2\lambda}}^8$
and define $\hat{T} \deq \Big(\hat{c}_1^\mathit{ch}, \hat{c}_2^\mathit{ch}, 1, 1, \lfloor (t \cdot \mathit{ch})/\ell \rfloor\Big) \in \GG^4 \times \ZZ$, \AlgSep
\> set $\Zv_q \deq \hat{T} \cdot \phi(\lfloor \hat{\rv}/\ell \rfloor) \in \GG^4 \times \ZZ$, \AlgSep
\lnum \label{ln:computeR}
\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
\end{alg}
We show the simulated transcript is distributed statistically close
to an accepting transcript of a real protocol execution.
Because $\ell$ does not divide $\abs{\GG}$ with overwhelming probability,
we know that $c_1$ and $c_2$ are uniform in $\GG$. 
Hence, observe that $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
exactly as in a real transcript.  It remains to show that the same holds
for $\zv_\ell, \Zv_q$, and $\Rv$. 
In an interaction with a real prover 
the vector $\rv$ is chosen uniformly in $\range{2^{2\lambda}}^8$.
Consider one value $r \rgets \range{2^{2\lambda}}$.
Because $2^{2\lambda}$ is much larger than $\ell$
we know that the pair 
$\big(\lfloor r/\ell \rfloor,\ (r \bmod \ell) \big)$
is statistically close to uniform in $\range{2^{2\lambda}/\ell} \times \range{\ell}$.
It directly follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
in a real transcript, is statistically close to uniform 
in $\range{\ell}^8$, as in the simulation.

Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly. 
Write $\hat{\rv}$ generated on line~\eqref{ln:randv} in the simulation
as $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$.
Then the simulated $\Zv_q$ is computed as:
\begin{equation} \label{eq:sim}
\Zv_q \deq \left(\begin{array}{l}
Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
Z_5 \gets \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2}/\ell \rfloor - \lfloor r_\text{na}/\ell \rfloor 
\end{array}\right) \in \GG^4 \times \ZZ.  
\end{equation}
Let's start with $Z_5 \in \ZZ$.  
In a real transcript 
$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
Therefore, because $\mathit{w2} - \mathit{na} = t$, we have
that $Z_5$ in a real transcript satifies
\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor - \Delta \]
where $\Delta \in \{0, 1\}$. 
In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
and $\lfloor r_\text{na} / \ell \rfloor$ 
are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
as in the the simulated $Z_5$ in~\eqref{eq:sim}.
The only difference is that the real distribution is shifted by $\Delta$
where as the simulated distribution is not.  
Because $\Delta$ is small, $\Delta \in \{0,1\}$,
this difference only negligibly affects the statistical distance
between the real and simulated distributions. 
We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
is statistically close to its real distribution.

Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
also simulated correctly. 
For example, in a real transcript 
\begin{align*}
    Z_1 & \deq g^{\lfloor (\mathit{ch}\cdot w + r_\text{w}) / \ell \rfloor} \cdot 
             h^{\lfloor (\mathit{ch}\cdot \mathit{s1} + r_\text{s1}) / \ell \rfloor} = \\
       & =   g^{\lfloor (\mathit{ch}\cdot w) / \ell \rfloor} \cdot
             h^{\lfloor (\mathit{ch}\cdot s1) / \ell \rfloor} \cdot
             g^{\lfloor r_\text{w} / \ell \rfloor - \Delta_\text{w}} \cdot 
             h^{\lfloor r_\text{s1} / \ell \rfloor - \Delta_\text{s1}} =  \\
       & = (\tilde{c}_1)^\mathit{ch} \cdot
             g^{\lfloor r_\text{w} / \ell \rfloor} \cdot 
             h^{\lfloor r_\text{s1} / \ell \rfloor} \cdot 
             \left[ (g^{1/\ell})^{\delta_\text{w} - \ell \cdot \Delta_\text{w}} \cdot 
               (h^{1/\ell})^{\delta_\text{s1} - \ell \cdot \Delta_\text{s1}} \right].
\end{align*}
where $\Delta_\text{w}, \Delta_\text{s1} \in \{0,1\}$
and $\delta_\text{w} \deq ((\mathit{ch} \cdot w) \bmod \ell) \in \range{\ell}$
and $\delta_\text{s1} \deq ((\mathit{ch} \cdot \mathit{s1}) \bmod \ell) \in \range{\ell}$.
Hence, $Z_1$ in a real transcript is distributed as 
the simulated $Z_1$ in~\eqref{eq:sim}, where the only
difference is the quantity 
$\Delta \deq (g^{1/\ell})^{\delta_\text{w} - \ell \cdot \Delta_\text{w}} \cdot 
               (h^{1/\ell})^{\delta_\text{s1} - \ell \cdot \Delta_\text{s1}} \in \GG$. 
We claim that this $\Delta$ only negligibly affects the statistical distance
between the real and simulated distributions. 
{\bf TODO:} explain why.

>>>>

\begin{proof}
The simulator takes $(c, t)$ as input and outputs the simulated transcript
$(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$ as follows:
\begin{alg}
\> choose random $\hat{c}_1, \hat{c}_2 \rgets \GG,\ \ \ell \rgets \primes$, and
$\mathit{ch} \rgets \range{2^\lambda}$, \AlgSep
\> set $c_1 \gets \hat{c}_1^\ell$ and $c_2 \gets \hat{c}_2^\ell$, \AlgSep
\> choose random $\zv_\ell \rgets \range{\ell}^8$, \AlgSep
\lnum \label{ln:randv}
\> choose random $\hat{\rv} \rgets \range{2^{2\lambda}}^8$
and define $\hat{T} \deq \Big(\hat{c}_1^\mathit{ch},\ \hat{c}_2^\mathit{ch},\ 1,\ 1,\ \lfloor (t \cdot \mathit{ch})/\ell \rfloor\Big) \in \GG^4 \times \ZZ$, \AlgSep
\> set $\Zv_q \deq \hat{T} \cdot \phi(\lfloor \hat{\rv}/\ell \rfloor) \in \GG^4 \times \ZZ$, \AlgSep
\lnum \label{ln:computeR}
\> compute $\Rv \deq \Zv_q^\ell \cdot \phi(\zv_\ell) / T^\mathit{ch} \in \GG^4 \times \ZZ$, \AlgSep
\> output $(c_1, c_2, \Rv, \ell, \mathit{ch}, \Zv_q, \zv_\ell)$.
\end{alg}
We show the simulated transcript is distributed statistically close
to an accepting transcript of a real protocol execution.
Because $\ell$ does not divide $\abs{\GG}$ with overwhelming probability,
we know that $c_1$ and $c_2$ are uniform in $\GG$. 
Hence, observe that $c_1, c_2, \ell, \mathit{ch}$ are all distributed 
exactly as in a real transcript.  It remains to show that the same holds
for $\zv_\ell, \Zv_q$, and $\Rv$. 
In an interaction with a real prover 
the vector $\rv$ is chosen uniformly in $\range{2^{2\lambda}}^8$.
Consider one value $r \rgets \range{2^{2\lambda}}$.
Because $2^{2\lambda}$ is much larger than $\ell$
we know that the pair 
$\big(\lfloor r/\ell \rfloor,\ (r \bmod \ell) \big)$
is statistically close to uniform in $\range{2^{2\lambda}/\ell} \times \range{\ell}$.
It directly follows that $\zv_\ell$, which is masked by $(\rv \bmod \ell)$
in a real transcript, is statistically close to uniform 
in $\range{\ell}^8$, as in the simulation.

Next we argue that $\Zv_q \in \GG^4 \times \ZZ$ is simulated correctly. 
Write $\hat{\rv}$ generated on line~\eqref{ln:randv} in the simulation
as $\hat{\rv} = \big(r_\text{w}, r_\text{w2}, r_\text{s1}, r_\text{a}, r_\text{na}, r_\text{s1w}, r_\text{sa}, r_\text{s2} \big)$.
Then the simulated $\Zv_q$ is computed as:
\begin{equation} \label{eq:sim}
\Zv_q \deq \left(\begin{array}{l}
Z_1 \gets \hat{c}_1^\mathit{ch} \cdot g^{\lfloor r_\text{w}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1}/\ell \rfloor} ,\quad
Z_2 \gets \hat{c}_2^\mathit{ch} \cdot g^{\lfloor r_\text{a}/\ell \rfloor} \cdot h^{\lfloor r_\text{s2}/\ell \rfloor} , \AlgSep
Z_3 \gets g^{\lfloor r_\text{w2}/\ell \rfloor} \cdot h^{\lfloor r_\text{s1w}/\ell \rfloor} / \hat{c}_1^{\lfloor r_\text{w}/\ell \rfloor},\quad
Z_4 \gets g^{\lfloor r_\text{na}/\ell \rfloor} \cdot h^{\lfloor r_\text{sa}/\ell \rfloor} / \hat{c}^{\lfloor r_\text{a}/\ell \rfloor}, \AlgSep
Z_5 \gets \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2}/\ell \rfloor - \lfloor r_\text{na}/\ell \rfloor 
\end{array}\right) \in \GG^4 \times \ZZ.  
\end{equation}
Let's start with $Z_5 \in \ZZ$.  
In a real transcript 
$Z_5 \deq \lfloor (\mathit{w2} \cdot \mathit{ch} + r_\text{w2})/\ell \rfloor -
          \lfloor (\mathit{na} \cdot \mathit{ch} + r_\text{na})/\ell \rfloor$.
Therefore, because $\mathit{w2} - \mathit{na} = t$, we have
that $Z_5$ in a real transcript satifies
\[    Z_5 = \lfloor (t \cdot \mathit{ch})/\ell \rfloor + \lfloor r_\text{w2} / \ell \rfloor - \lfloor r_\text{na} / \ell \rfloor + \Delta \]
where $\Delta \in \{0, \pm 1\}$. 
In a real transcript $\lfloor r_\text{w2} / \ell \rfloor$ 
and $\lfloor r_\text{na} / \ell \rfloor$ 
are statistically close to fresh uniform values in $\range{2^{2\lambda}/\ell}$, 
as in the the simulated $Z_5$ in~\eqref{eq:sim}.
The only difference is that the real distribution is shifted by $\Delta$
where as the simulated distribution is not.  
However this $\Delta$ only negligibly affects the statistical distance
between the real and simulated distributions. 
The reason is that in both distributions 
every possible value in the range of $Z_5$, 
except possibly at the edges, 
is obtained from exactly $\ell^2$ values of $(r_\text{w2}, r_\text{na})$. 
We thus conclude that the simulated $Z_5$ in~\eqref{eq:sim} 
is statistically close to its real distribution.

Essentially the same argument shows that $Z_1, Z_2, Z_3, Z_4$ are
also simulated correctly. 
For example, in a real transcript 
\begin{align*}
    Z_1 & \deq g^{\lfloor (\mathit{ch}\cdot w + r_\text{w}) / \ell \rfloor} \cdot 
             h^{\lfloor (\mathit{ch}\cdot \mathit{s1} + r_\text{s1}) / \ell \rfloor} = \\
       & =   g^{\lfloor (\mathit{ch}\cdot w) / \ell \rfloor} \cdot
             h^{\lfloor (\mathit{ch}\cdot s1) / \ell \rfloor} \cdot
             g^{\lfloor r_\text{w} / \ell \rfloor + \Delta_\text{w}} \cdot 
             h^{\lfloor r_\text{s1} / \ell \rfloor + \Delta_\text{s1}} =  \\
       & = (\tilde{c}_1)^\mathit{ch} \cdot
             g^{\lfloor r_\text{w} / \ell \rfloor} \cdot 
             h^{\lfloor r_\text{s1} / \ell \rfloor} \cdot 
             \left[ (g^{1/\ell})^{\delta_\text{w} + \ell \cdot \Delta_\text{w}} \cdot 
               (h^{1/\ell})^{\delta_\text{s1} + \ell \cdot \Delta_\text{s1}} \right]
\end{align*}
where $\Delta_\text{w}, \Delta_\text{s1} \in \{0,1\}$ as for $Z_5$, 
and $\delta_\text{w} \deq (\mathit{ch} \cdot w \bmod \ell) \in \range{\ell}$
and $\delta_\text{s1} \deq (\mathit{ch} \cdot \mathit{s1} \bmod \ell) \in \range{\ell}$.
Hence, $Z_1$ in a real transcript is distributed as 
the simulated $Z_1$ in~\eqref{eq:sim}, where the only
difference is the quantity 
$\Delta \deq (g^{1/\ell})^{\delta_\text{w} - \ell \cdot \Delta_\text{w}} \cdot 
               (h^{1/\ell})^{\delta_\text{s1} - \ell \cdot \Delta_\text{s1}} \in \GG$. 
We claim that this $\Delta$ only negligibly affects the statistical distance
between the real and simulated distributions. 
{\bf TODO:} explain why.
